FoRTE baseline

### 2019-06-19 analysis/paper/paper.Rmd
Update `drake.R` for new outputs and figures

```{r bigfacet-plot, fig.cap = bigfacet_cap, fig.dim = c(12, 12)}
bigfacet_cap <- paste(
  "ED2 PFT-level predictions of leaf area index (LAI) by model configuration and parameterization."
)
readd(bigfacet_plot)
```

>>>>

```{r bigfacet-plot, fig.cap = bigfacet_cap, fig.dim = c(12, 12)}
bigfacet_cap <- paste(
  "ED2 PFT-level predictions of leaf area index (LAI) by model configuration and parameterization."
)
readd(lai_pft_plot)
```
